Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-03-08 paper.tex
First paragraphs in dataset

% Define subjects.

@@

what is specific to our problem compared to regular collaborative filtering:
%+ subjects are equivalent to users. Not all subjects have the same input data. Anatomical variability, acquisition variability (e.g., 1 subject may have multiple T1s).
%+ files are produced in a specific order (movies aren't),
% which add constraints on the training set (cannot sample late files and not early ones).
%+ utility matrix is not sparse: we can potentially populate it completely. Which means that we can decide precisely which samples we need (active sampling). Therefore we can take the first row and first column to avoid cold start issues.

@@

>>>>

% Define subjects, pipelines.

@@

% What is specific to our problem compared to regular collaborative filtering:
%+ subjects are equivalent to users. Not all subjects have the same input data. Anatomical variability, acquisition variability (e.g., 1 subject may have multiple T1s).
%+ files are produced in a specific order (movies aren't),
% which add constraints on the training set (cannot sample late files and not early ones).
%+ utility matrix is not sparse: we can potentially populate it completely. Which means that we can decide precisely which samples we need (active sampling). Therefore we can take the first row and first column to avoid cold start issues.

@@

We acquired data about the computational reproducibility of analysis
pipelines of the Human Connectome Project~\cite{general-hcp}. We
processed a set S of 94 subjects randomly selected in the S500 HCP
release~\todo{URL} in three execution conditions with different
versions of the CentOS operating system (5.?, 6.? and 7.?), using the
PreFreesurfer, Freesurfer, PostFreesurfer and fMRIVolume pipelines
described in~\cite{hcp-pipelines} and available at \todo{URL}. For
each pipeline, we identified the set F of files produced for all
subjects in all conditions. For each condition pair and each pipeline,
we computed a binary difference matrix D of size $|F|\times|S|$, where $D_{i,j}$ is true
if file $i$ of subject $j$ was different in each condition. Rows of
$M$ are ordered by ascending file modification time in the pipeline.

Figure~\ref{fig:pre-freesurfer-5-7} shows the difference matrix
obtained for the PreFreesurfer pipeline\todo{Remove title from figure,
  remove color scale, add axes labels.}. The computational
reproducibility of the PreFreesurfer pipeline varies across subjects,
which motivates our study. Nevertheless, some files behave
consistently across all subjects, leading to complete black or white
lines. The ratio of positive elements in this matrix is
\todo{x}\%. Similar matrices were obtained with this pipeline for
CentOS~6 vs CentOS~7 and for CentOS~5 vs CentOS~6, see
Figures~\ref{fig:pre-freesurfer-5-6} and~\ref{fig:pre-freesurfer-5-7}.

\begin{figure}
  \includegraphics[width=\columnwidth]{figures/original_matrix_CentOS5vsCentOS7.pdf}
  \caption{Difference matrix, PreFreesurfer pipeline, CentOS~5 vs CentOS~7.}
  \label{fig:pre-freesurfer-5-7}
\end{figure}
